\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{mathptmx}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{multicol}

% Page setup
\geometry{
    left=1.5cm,
    right=1.5cm,
    top=1.5cm,
    bottom=1.5cm
}
\pagestyle{empty}

% Minimal spacing
\setstretch{1.0}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.1em}  % Very small paragraph spacing
% Compact section formatting
\titlespacing*{\section}{0pt}{0.4em}{0.2em}
% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}
\titleformat{\subsubsection}{\normalsize\bfseries}{}{0em}{}

\setlist[itemize]{leftmargin=1em, itemsep=0pt, topsep=0pt}

\begin{document}

% Header
\begin{center}
    {\LARGE \textbf{Hai Kuo (Ezra) Lu}}\\[0.5em]
    Applied AI engineer focused on statistical modeling, large-model deployment, and high-performance systems.\\
    Experienced in nonlinear models, agent frameworks, and document parsing with C++/Python implementations.\\[0.5em]
    \rule{\textwidth}{0.4pt}
\end{center}

\begin{multicols}{2}

\section{Education}

\subsection{Boston University}
\textbf{Master of Arts in Statistics} \hfill Boston, MA\\
College of Math and Statistics \hfill GPA: 3.58/4.0\\
\textit{2018.09 -- 2020.01}
\begin{itemize}[leftmargin=1em, itemsep=0pt]
    \item Core Coursework: Statistical Learning, General Linear Regression, Bayesian Statistics, Computational Statistics, Stochastic Process
\end{itemize}

\subsection{Beijing Institute of Technology}
\textbf{Bachelor of Science in Statistics} \hfill Beijing, China\\
School of Mathematics and Statistics \hfill GPA 3.3/4.0\\
\textit{2014.09 -- 2018.06}
\begin{itemize}[leftmargin=1em, itemsep=0pt]
    \item Core Coursework: Mathematical Analysis, Advanced Algebra, Real Analysis, Probability Theory, Mathematical Statistics, C Programming
\end{itemize}

\section{Work Experience}

\subsection{Bojia Pharmaceutical Technology Co., Ltd.}
\textbf{Mid-level Algorithm Researcher} \hfill Shanghai \hfill 2023.08 -- Present
\begin{itemize}[leftmargin=1em, itemsep=0pt]
    \item Reproduced cutting-edge NLME algorithms (paper $\rightarrow$ Python demo $\rightarrow$ C++) with parity against industry standards.
    \item Designed test suites and simulation pipelines to validate algorithm accuracy across dosing regimens and PK/PD structures.
    \item Optimized performance by eliminating redundant computations and replacing Eigen routines with BLAS/LAPACK, achieving 70\%+ speedups.
\end{itemize}

\subsection{Zhejiang LaiFuture Technology Co., Ltd.}
\textbf{Data Scientist, Intelligent Data Department} \hfill 2021.07 -- 2023.08
\begin{itemize}[leftmargin=1em, itemsep=0pt]
    \item Led healthcare AI collaborations, covering data collection, model development, and deployment for hospital research needs.
    \item Built automated data ingestion/cleaning pipelines tailored to heterogeneous hospital information systems and formats.
    \item Processed multimodal medical data (signals, imaging) using ResNet and CNN architectures to deliver robust feature extraction.
\end{itemize}

\section{Projects}

\subsection{FOCE and SAEM Algorithm Suite}
\begin{itemize}[leftmargin=1em, itemsep=0pt]
    \item Implemented FOCEI and SAEM NLME parameter estimation algorithms from scratch, including Hessian approximations and optimizer integration.
    \item Accelerated gradient computations via analytic/numeric hybrid strategies, reducing iteration time by \textasciitilde{}30\%.
    \item Engineered reusable matrix/tensor structures with memory pooling to remove Eigen allocation bottlenecks in large simulation workloads.
    \item Benchmarked outputs against NONMEM/Monolix across diverse model structures to ensure precision and robustness.
\end{itemize}

\subsection{LLM-Powered PDF Structuring and Auto-labeling}
\begin{itemize}[leftmargin=1em, itemsep=0pt]
    \item Designed an end-to-end pipeline that converts PDF documents into normalized JSON layouts before LLM processing.
    \item Integrated private deployments of Dolphin and DeepSeek-R1 for entity extraction, prompt orchestration, and agent-style workflows.
    \item Delivered a production system that dramatically reduced manual labeling time while improving accuracy for clinical statistics teams.
\end{itemize}

\section{Skills}
\begin{itemize}[leftmargin=1em, itemsep=0pt]
    \item \textbf{Languages}: Python, C++, R, Bash, SQL
    \item \textbf{Frameworks}: PyTorch, NumPy, Pandas, Polars, Scikit-learn, Eigen, SymPy, OpenBLAS/LAPACK
    \item \textbf{Modeling}: FOCEI, SAEM, Bootstrap, NLME, Bayesian Inference
    \item \textbf{Publications}: PAGE 31 (2023) Abstract 10676 \href{https://www.page-meeting.org/?abstract=10676}{www.page-meeting.org/?abstract=10676}
    \item \textbf{Languages}: Native Chinese, Fluent English (TOEFL 110)
\end{itemize}

\end{multicols}

\end{document}
